API design for machine learning software: experiences from the scikit-learn project

### 2013-09-09 paper.tex
standard article format

\documentclass[10pt,twocolumn]{article}

\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{minted}

@@

%\pagestyle{headings}

@@

@@

\begin{abstract}
\sklearn is an increasingly popular machine learning library
for the Python programming language.
It is designed to be simple and efficient,
accessible to non-experts, and reusable in various contexts:
it has a user base in neuroscience, astronomy, computational linguistics,
as well as industry.

In this paper, we present and
discuss our design choices for the application programming interface (API) of
the project. In particular, we describe the simple and elegant interface shared
by all learning and processing units in the library and then discuss its
advantages in terms of composition and reusability. The paper also comments on
implementation details specific to the Python ecosystem and analyzes obstacles
faced by users and developers of the library.\footnote{
  An earlier version of this paper was presented
  at the ECML/PKDD Workshop on Languages for Data Mining and Machine Learning,
  September 2013, Prague.}
\end{abstract}

%\setcounter{footnote}{0}

>>>>

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{authblk}
%\usepackage{hyperref}
\usepackage{minted}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}

@@

\pagestyle{headings}

@@

\date{}

@@

\sklearn is an increasingly popular machine learning
library. Written in Python, it is designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this paper, we present and
discuss our design choices for the application programming interface (API) of
the project. In particular, we describe the simple and elegant interface shared
by all learning and processing units in the library and then discuss its
advantages in terms of composition and reusability. The paper also comments on
implementation details specific to the Python ecosystem and analyzes obstacles
faced by users and developers of the library.
